Efficient Handling of String-Number Conversion

### 2019-11-22 draft.tex
added citation on Ecmascript

A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indices are converted to strings. This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}). Therefore, any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly. Consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:

>>>>

A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indices are converted to strings. This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{ecmascript2019ecmascript} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}). Therefore, any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly. Consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
